Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-29 Ch1_movement_rates/Ch1_Figures.Rmd
Figure 6 ready

@@

nsamps <- 10000
itera <- 1000

@@

```{r fig.width=12, fig.height=3}
# Threshold figures

@@

  thresh_data %>%
    ggplot(., aes(y = t.scale, x = u.i)) +
    geom_point(shape = 1, size = 2) +
    # geom_line(linetype = "dashed") +
    geom_linerange(aes(x = u.i, ymin = low.t.scale, ymax = up.t.scale)) +
    labs(title = paste(model, "threshold =", th, "m"), 
         x = "Threshold in meters", y = "Scale") +
    theme_bw() +
    geom_vline(xintercept = th, color = "red", linetype = "dashed") +
    scale_x_continuous(limits = r, n.breaks = 7 ) +
    # scale_x_continuous(name = NULL, labels = NULL, breaks = NULL) +
    # theme(axis.title.x = element_blank(),
    #       axis.ticks.x = element_blank(),
    #       axis.text.x = element_blank()) +
    # coord_cartesian(xlim = c(200, 550)) +
    NULL -> thresh_scale

@@

  plot_grid(thresh_scale, thresh_shape, nrow = 2)

@@

plot_grid(plot.cp, plot.pp, plot.np, ncol = 3)
ggsave2(filename = "Ch1_movement_rates/Figures/Figure6.png")

>>>>

disp_table %>% 
  dplyr::select(., Model, Mean.dispersal_sd, kurtosis, Max_dispersal, LDD_500) -> disp_table

@@

nsamps <- 10000

@@

```{r fig.width=12, fig.height=4}
# Threshold figures

@@

  thresh_data %>%
    ggplot(., aes(y = t.scale, x = u.i)) +
    geom_point(shape = 1, size = 2) +
    # geom_line(linetype = "dashed") +
    geom_linerange(aes(x = u.i, ymin = low.t.scale, ymax = up.t.scale)) +
    labs(title = paste(model, "threshold =", th, "m"), 
         x = "Threshold in meters", y = "Scale") +
    theme_bw() +
    geom_vline(xintercept = th, color = "red", linetype = "dashed") +
    scale_x_continuous(limits = r, n.breaks = 7 ) +
    # scale_x_continuous(name = NULL, labels = NULL, breaks = NULL) +
    theme(axis.title.x = element_blank(),
          #axis.ticks.x = element_blank(),
          axis.text.x = element_blank()) +
    # coord_cartesian(xlim = c(200, 550)) +
    NULL -> thresh_scale

@@

  plot_grid(thresh_scale, thresh_shape, nrow = 2, align = "v")

@@

plot_grid(plot.cp, plot.pp, plot.np, ncol = 3, labels = c("A)", "B)", "C)"), hjust = 0, vjust = 1, label_size = 10)
#ggsave2(filename = "Ch1_movement_rates/Figures/Figure6.png")
